---
title: "Assignment 4"
author: "Juntong Wei, Qin Xu, Xuanming Liang, Ziang Li"
date: "`r Sys.Date()`"
linestretch: 1.5
output: 
  bookdown::html_document2: 
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    keep_tex: yes
    number_sections: yes
    toc: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      messages = FALSE, 
                      warning = FALSE)
```

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(broom)
library(countrycode)
library(tidytext)
library(viridis)
library(rworldmap)
library(ggmap)
library(maps)
library(sp)
library(maptools)
library(readr)
library(ggraph)
library(igraph)
library(RColorBrewer)
library(gganimate)
library(gifski)
library(ggalluvial)
library(hrbrthemes)
library(kableExtra)
library(leaflet)
library(scales)
library(grid)
library(gridExtra)
library(bookdown)
```

```{r, message=FALSE, warning=FALSE}
data <- read_csv("data/athlete_events.csv")
dat1 <- read_csv("data/countries.csv")
```

# Introduction

This report looks at the data from previous Olympic Games and finds some interesting points. It focuses on the number of medals, the age of the athletes, the gender, the country and the relationship between them. It focuses on the distribution and number of medals, the ranking of countries in terms of the number of medals won, the number of Olympic sports and the relationship between gender, age and medals won. In this report, we use two datasets, named "data" and "dat1". In "data" has 271,116 obs. and 15 variables. In "dat1" has 184 obs. And five variables. In "dat1", we mainly use to replace the country code (NOC) with the name of the country, so we use the variables "NOC" and "Country". In "data" is the main dataset we use, we use "sex", "age", "NOC", "Year", "sport", "event" and "medal" these seven variables, and the variables used them in four parts of the study.

# Analysis

## Medal distribution by country (Xuanming_Liang)

```{r, message=FALSE, warning=FALSE}
medal <- data %>%
  filter(!is.na(Medal))

team<- medal %>% 
  group_by(NOC) %>% 
  summarise(Gold =  sum (Medal == "Gold"),
            Silver = sum (Medal == "Silver"),
            Bronze = sum (Medal == "Bronze"))
```

```{r, message=FALSE, warning=FALSE}
team_M <- team %>%
  pivot_longer(!"NOC", names_to = "medals", values_to = "number_of_medals")

country_M <- countrycode(team_M$NOC, "ioc", "country.name")

country_M <- data_frame(country_M, team_M)
country_M<- na.omit(country_M)
```

```{r, message=FALSE, warning=FALSE}
team_T <- cbind(team, c(rowSums(team [, 2:4], na.rm = TRUE))) 
colnames(team_T)[5] <- "Total"

country_T <- countrycode(team_T$NOC, "ioc", "country.name")

country_T <- data_frame(country_T, team_T)
country_T<- na.omit(country_T)

country_T <- country_T %>%
  arrange(desc(Total)) %>% 
  rename("Country" = country_T)

country_T_10 <- country_T%>% 
  top_n(10)

knitr::kable(country_T_10, caption = "The medals in different country", col.names = c("Country",  "NOC", "Gold", "Silver", "Bronze", "Total"))
```

```{r, message=FALSE, warning=FALSE}
ct <- inner_join(country_T, dat1, by = "Country")
```

```{r, message=FALSE, warning=FALSE}
world <- map_data("world")
visit.x<-ct$Longitude
visit.y<-ct$Latitude
```

```{r map, fig.cap="Medals distribution in the world wide", message=FALSE, warning=FALSE}
hex_codes <- hue_pal(h=c(180,270)) (length(ct$Country)) 
pal <- colorFactor(hex_codes, domain = ct$Country)

mytext <- paste(
   "Country: ", ct$Country, 
   "Total: ", ct$Total, 
   "Gold: ", ct$Gold,
   "Silver: ", ct$Silver,
   "Bronze: ", ct$Bronze) %>%
  lapply(htmltools::HTML)

map <- leaflet(ct) %>% 
  addTiles() %>%
  addCircles(
    lng = ~Longitude,
    lat = ~Latitude,
    radius = ~Total*300,
    stroke = F,
    fillOpacity = 0.4,
    color = ~pal(Country),
    label = mytext
  ) 
map
```

The map \@ref(fig:map) shows the number of medals won by each country in the world at the Olympic Games, including gold, silver, bronze and total. The size of the circles on the map indicates the number of medals won, so it is easy to see that the USA has the most medals. Europe has the highest number of medals, and the density of the circles shows that most European countries have won medals and have accumulated a significant number of medals in total.


## Find out which sport has the largest number of participants and study the distribution of gold MEDALS in different countries over time (Juntong_Wei)

```{r, message=FALSE, warning=FALSE}
sport_count<- data %>% 
  mutate(Number_of_people_in_each_sport = Sport) %>% 
  count(Number_of_people_in_each_sport) %>% 
  top_n(10) 
```

```{r wei1, fig.cap="Top 10 sports with the most athletes", fig.align='center', message=FALSE, warning=FALSE}
sport_count %>% 
  mutate(Number_of_people_in_each_sport = fct_reorder(Number_of_people_in_each_sport, n)) %>% 
  ggplot(aes(x = Number_of_people_in_each_sport, 
             y = n, 
             fill = Number_of_people_in_each_sport)) + 
  coord_flip() + 
  geom_text(aes(x = Number_of_people_in_each_sport,  
                y = n + 4000,
                label = n)) + 
  geom_col() + 
  xlab("Sport") +
  ylab("Number of people in each sport") + 
  theme(strip.text = element_text(size = 10), 
        axis.text = element_text(size = 10), 
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0.15),
        axis.title.x = element_text(size = 15), 
        axis.title.y = element_text(size = 15))
```

With the Figure \@ref(fig:wei1), It illustrate the number of participants in different sports, and select the top 10 of them, according to the figure, the most popular sports is **Athletics** which is 38,624. the second is **gymnastics** and the third one is **swimming**. the fine thing about this figure is that the number of participate athletes of first 3 sport is far more than any other sports. 

```{r, message=FALSE, warning=FALSE}
Athletics_1 <- data %>% 
  filter(Sport == "Athletics" & Medal == "Gold")%>% 
  select(Sport, NOC, Medal, Year) %>% 
  cbind(1) %>% 
  rename("Number" = "1") %>% 
  group_by(NOC, Year) %>%
  summarise(Total = sum(Number)) %>% 
  mutate(Accumu = cumsum(Total)) 

Athletics <- inner_join(Athletics_1, country_T, by="NOC")
```

```{r, message=FALSE, warning=FALSE}
ranking <- Athletics %>%
  group_by(Year) %>%
  mutate(rank = rank(-Accumu),
         Accumu_rel = Accumu/Accumu[rank==1],
         Accumu_lbl = paste0(" ",round(Accumu/1e9))) %>%
  group_by(Country) %>% 
  filter(rank <=5) %>%
  ungroup()
```

```{r wei2, fig.cap="In the Athletics sports, the ranking of first 5 contries about Total number of Cumulative gold MEDALS won ", fig.align='center', message=FALSE, warning=FALSE}
ggp <- ggplot(ranking, 
              aes(x = rank, 
                  y = Accumu, 
                  group = Country)) +
  geom_bar(stat = "identity", 
           aes(fill = Country)) +
  transition_states(Year, transition_length = 2, state_length = 0) +
ease_aes('quadratic-in-out') +  
  enter_drift(x_mod = -1) + exit_drift(x_mod = 1) +
  labs(x = "Ranking of the gold medal accumulated",
       y = "Accumulated Number of gold medal",
       title = "Year {closest_state}")

animate(ggp, 200, fps = 20,  width = 1200, height = 1000, 
        renderer = gifski_renderer("gganim.gif"))
```

Then we focus on the athletics sports, the above Figure \@ref(fig:wei2) describes only in the Athletics sports, it shows number of Cumulative gold MEDALS won in each country and ranking them. The x-axis is about first 5 ranking, the y-axis is about the Accumulated Number of gold medal, and the different color means different countries, so there are 2 interesting finding in this GIF, 

- The American is always number one in the ranking list except year 1980. That's because the USA did not join the sport meet in that year to boycott the former Soviet Union. 

- Sometimes the bar overlapped on the x-axis, which means it shares the same ranking place in this year. 


## How about the Medals of top 5 countries allocated in the events (Ziang_Li)

In the section 1, we discussed the number of medals each country has won in the previous Olympic Games. In section2, we analyzed the sports with the largest number of athletes participate in. Hence, in section3, we will compare the five countries with the most medals and the distribution of medals in the five events with the largest number of participants.

From the figure \@ref(fig:LI1), it clearly shows that the Medals changing of the Top5 countries in previous Olympic Games.  The United States has consistently ranked first in the total number of medals. After 1990, the number of medals in Germany has increased rapidly. And in 1998, Germany ranked second in the total number of medals.

From the figure \@ref(fig:LI2), it shows the distribution of the top5 countries medals among the 5 sports with the most participants. The number of medals in the United States is larger than the other four countries and The United States has an absolute advantage in swimming events, especially in the relay race events. The medals of United Kingdom are more distributed in Cycling. In addition, the medals from other countries are very evenly distributed among the five events

```{r, message=FALSE, warning=FALSE}
top1 <- country_T %>%
  top_n(5)

aa <- sport_count %>% 
  arrange(desc(n)) %>% 
  top_n(5)

ttt <- top1 %>% 
  inner_join(data, top1, by="NOC") %>% 
  filter (!is.na (Medal)) %>% 
  filter ( Sport == "Athletics" | Sport == "Gymnastics" | Sport == "Swimming" | Sport == "Shooting" | Sport == "Cycling") %>% 
  select (Country, Sport, Event, Medal) %>% 
  group_by(Country, Sport, Event, Medal) %>% 
  tally() %>% 
  ungroup() %>% 
  group_by(Country, Sport, Event) %>% 
  summarise( n = sum(n)) 

Athletics <- ttt %>% 
  ungroup() %>% 
  filter(Sport == "Athletics") %>% 
  group_by(Event) %>% 
  summarise( tot = sum(n)) %>% 
  arrange(desc(tot)) %>% 
  top_n(5)

Cycling <- ttt %>% 
  ungroup() %>% 
  filter(Sport == "Cycling") %>% 
  group_by(Event) %>% 
  summarise( tot = sum(n)) %>% 
  arrange(desc(tot)) %>% 
  top_n(5)

Gymnastics <- ttt %>% 
  ungroup() %>% 
  filter(Sport == "Gymnastics") %>% 
  group_by(Event) %>% 
  summarise( tot = sum(n)) %>% 
  arrange(desc(tot)) %>% 
  top_n(5)

Shooting <- ttt %>% 
  ungroup() %>% 
  filter(Sport == "Shooting") %>% 
  group_by(Event) %>% 
  summarise( tot = sum(n)) %>% 
  arrange(desc(tot)) %>% 
  top_n(5)

Swimming <- ttt %>% 
  ungroup() %>% 
  filter(Sport == "Swimming") %>% 
  group_by(Event) %>% 
  summarise( tot = sum(n)) %>% 
  arrange(desc(tot)) %>% 
  top_n(5)

rrr <- rbind(Athletics, Cycling, Gymnastics, Shooting, Swimming) 

ooo <- left_join(rrr, ttt, by="Event") 

```

```{r, message=FALSE, warning=FALSE}
qqq <- data %>% 
  filter(!is.na(Medal)) %>%
  select (NOC, Year, Medal)%>% 
  cbind (1) %>% 
  rename( "Number" = "1") %>% 
  select(NOC, Year, Number) 

qqq <- left_join(qqq, country_T) 

www <- qqq %>% 
  select(Country, Year, Number) %>% 
  group_by(Country, Year) %>% 
  summarise( number = sum(Number)) %>% 
  mutate(total = cumsum(number)) %>% 
  filter(Country == "United States" | Country == "Germany" | Country == "United Kingdom" | Country == "France" | Country == "Italy")

```

```{r LI1,fig.cap="Changes in the total number of medals of the top 5 countries in the previous Olympic Games", message=FALSE, warning=FALSE}
q <- ggplot(www, aes(x=Year, y=total, group=Country, color=Country)) +
    geom_line() +
    geom_point() +
    scale_color_viridis(discrete = TRUE) +
    ggtitle("Changes in the total number of medals of the top 5 countries in the previous Olympic Games") +
    theme_ipsum() +
    ylab("Number of the medals") +
    transition_reveal(Year)

animate(q, nframes = 350,fps = 25,  width = 1200, height = 1000, 
        renderer = gifski_renderer("yearly.gif"))
```

```{r LI2, fig.cap="Distribution of the top 5 Countries' medals among the 5 sports with the most participants", fig.height=15, fig.width=20, message=FALSE, warning=FALSE}
ggplot(as.data.frame(ooo),
       aes(y = n, axis1 = Country, axis2 = Sport, axis3 = Event)) +
  geom_alluvium(aes(fill = Country), width = 1/40) +
  geom_stratum(width = 1/50, fill = "white", color = "black") +
  geom_label(stat = "stratum", aes(label = after_stat(stratum)))+
  scale_x_discrete(limits = c("Country", "Sport", "Event"), expand = c(.05, .05)) +
  scale_fill_brewer(type = "qual", palette = "Set3") +
  ggtitle("Distribution of the top 5 Countries' medals among the 5 sports with the most participants")
```

## Compare the total medal won by different age for both female and male. (Qin_Xu)

According to @ elmenshawy2015rise, age at peak of athletics performance for women have increased in the last 20 years but not for men, hence in this section, we seek to compare the athletics performance of both gender by examining the medal results of athletes who attended Olympics from 1896 to 2016  by age and gender.

```{r data_wrangling1, message=FALSE, warning=FALSE}
clean_data <- data %>% 
  select (c("Sex","Age","Medal")) %>% 
  mutate(Sex=as.factor(Sex),
        Medal= as.factor(Medal)) %>% 
  group_by(Sex,Age) %>% 
  count(Medal) 

clean_data
```

```{r data_wrangling2}
clean_data1 <- clean_data %>% 
mutate(age_group = cut(Age,breaks = c(0,15,30,45,60,75,90))) %>% 
select(-Age) %>% 
  group_by(Sex,age_group) %>% 
  count(Medal) %>% 
  rename(number = "n")
clean_data1
```

```{r data_wrangling3, message=FALSE, warning=FALSE}
table1<- clean_data1 %>% 
    group_by (Sex,age_group) %>% 
  summarise(total_medal_in_age_group= sum(number))
  
table1
```
```{r table1,  eval = TRUE, echo = FALSE, warning=FALSE, message=FALSE}

percentage<- table1 %>% 
  group_by(Sex) %>% 
summarise(total_medal_by_sex =sum(total_medal_in_age_group)) %>% 
  left_join(table1, by ="Sex") %>% 
  mutate("Percentage" = ((total_medal_in_age_group/total_medal_by_sex)*100)) 

  knitr::kable (percentage ,caption = "compare the percentage of thetotal medal won by different age groups for both female and male") %>% kable_styling()
  
```
In Table \@ref(tab:table1) we compare the total medal won by different age groups for both female and male.

From this table, it shows that female younger athletes age range from 15- 30 has the highest percentage (32.09%) of total medal won compared to other age group, while older female athletes age from 60 to 75 has the least percentage of medal won (8.02%). However, for males athletes, it appears that age group between (15-30),(30-45),(45-60_ share the same percentage( and highest) of total medal won, while older male athletes age form 75 to 90 again has the least percentage of medal won ( 2.52%).

```{r figure1, fig.cap="The percentage of total medal won in different age group by sex", fig.height = 5, fig.width = 6, fig.align='center', eval = TRUE, echo = FALSE, warning=FALSE, message=FALSE}

plot <- ggplot(data = percentage, 
                      aes(x = age_group,
                          y= Percentage,
                          fill = Sex)) +
    geom_bar(stat="identity",position ="fill") +
    ggtitle("Total medal won by different age group for female and male ")
plot
```

In Figure \@ref(fig:figure1), we have plotted the percentage of the total medal won by different age group and compared in against both gender of male and female.

In Figure \@ref(fig:figure1),  depicts that for the age groups aged (0-15),(15-30),and (30-45), female athletes is accounted of  a higher proportion  of the total medal compared to males, However by the age group (45 to 60), males athletes exceed female athletes in the proportion of  total medal won and continues to have a higher proportion than female in the older age bracket. 

## Comparison of different medal distribution between age group by gender. (Qin_Xu)

```{r table2, message=FALSE, warning=FALSE}
clean_data2 <- data %>% 
  select (c("Sex","Age","Medal")) %>% 
  mutate(Sex=as.factor(Sex),
        Medal= as.factor(Medal)) %>% 
  group_by(Sex,Age) %>% 
  count(Medal) %>% 
  rename("number"=n) 
  clean_data2 


gold1<- clean_data2 %>% 
  filter(Medal== "Gold") %>% 
  group_by(Sex) %>% 
  summarise(total_silver_medal=sum(number)) 
gold<- clean_data2 %>% 
  filter(Medal== "Gold") %>% 
  left_join(gold1 ,by = "Sex") %>% 
  mutate("Percentage" = ((number/total_silver_medal)*100)) 
```

```{r table3, message=FALSE, warning=FALSE}
silver1<- clean_data2 %>% 
  filter(Medal== "Silver") %>% 
  group_by(Sex) %>% 
  summarise(total_silver_medal=sum(number)) 
silver<- clean_data2 %>% 
  filter(Medal== "Silver") %>% 
  left_join(silver1 ,by = "Sex") %>% 
  mutate("Percentage" = ((number/total_silver_medal)*100)) 
```

```{r table4, message=FALSE, warning=FALSE}
bronze1<- clean_data2 %>% 
  filter(Medal== "Bronze") %>% 
  group_by(Sex) %>% 
  summarise(total_bronze_medal=sum(number)) 
bronze<- clean_data2 %>% 
  filter(Medal== "Bronze") %>% 
  left_join(bronze1 ,by = "Sex") %>% 
  mutate("Percentage" = ((number/total_bronze_medal)*100)) 
```

```{r goldf, fig.cap = "The gold medal distribution between different age group for male and female ", fig.height = 5, fig.width = 6, fig.align='center', message=FALSE, warning=FALSE}
gold
gold_plot<- ggplot(data=gold, aes(  x= Age,
                                      y= Percentage,
                                      fill= Sex)) +
  geom_density (alpha = 0.4, stat = "identity", position = "identity")+

  ggtitle("The distribution of gold medal won by different age group for female and male")
```

```{r silverf,fig.cap = "The silver medal distribution between different age group for male and female ", fig.height = 5, fig.width = 6, fig.align='center', message=FALSE, warning=FALSE}

silver 
silver_plot<- ggplot(data=silver, aes(  Age,
                                      y= Percentage,
                                      fill= Sex)) +
   geom_density (alpha = 0.4, stat = "identity", position = "identity")+
  ggtitle("The distribution of silver medal won by different age group for female and male ")
```

```{r bronzef, fig.cap = "The bronze medal distribution between different age group for male and female ", fig.height = 5, fig.width = 6, fig.align='center', message=FALSE, warning=FALSE}
bronze
bronze_plot<- ggplot(data=bronze, aes(x=Age,
                                      y= Percentage,
                                      fill= Sex)) +
   geom_density (alpha = 0.4, stat = "identity", position = "identity")+
  ggtitle("The distribution of bronze medal won by different age group for female and male ")
```

```{r figure2, fig.cap="The medal distribution won in different age group by sex", fig.height = 5, fig.width = 6, fig.align='center', message=FALSE, warning=FALSE}

grid.arrange(gold_plot,silver_plot,bronze_plot, ncol=2)

```

n Figure \@ref(fig:figure2), the different medal distribution was plotted for different age and compared in against both gender of male and female.

From this plot. the gold medal distribution for female and male are positively skewed with the athletes in the younger age group accounting for more of the gold medals earned than the older athletes (specifically, both female and male athletes age in early 20s have the highest percentage of the gold medal won).Similar result could be seen for silver medal distribution, both distribution for female and male athlete are positively skewed, however we can see that the age group that account the most percentage of silver medal won is ranged from 20-30 years older for both female and male athletes. In the bronze medal distribution, it shares similar distribution as silver medal as athletes age from 20 to 30 is account for the most percentage of bronze medal won for both female and male. 
Additionally, it is seen that for all medal distribution, female athletes of younger age (0-20) tend to account for higher percentage of medal (gold, silver, and bronze) than male athletes, however by age 30 and over, male athletes exceed female athletes in medal won for gold, silver and bronze medal.  This could be due the quicker fall of physical, technical and strategics abilities of females athletes 30 and over , companied with increasing social pressure that female of an older age to be more family orientated.

Hence from the above analysis, we conclude that  in general for both gender, age 20 to 30 tends to account for most proportions of the medals (gold, silver, and bronze)won, furthermore, it was found that female athletes tends to do better than male for medal won before age20, however later was exceed by male after age 30.

# Conclusion  

In summary, from the presentation today, we conclude that for quesiton1 when comparing the distribution of medal in different country aound the world, America appears to have the most medals in the world. In addtional, for question two, we have found that the sport athletics have the largest number of athletics, and in this sports, The United States accumulated the most gold MEDALS in each year. 
Furthermore for question three, we conclude that The United States has an absolute advantage in swimming events,The medals of United Kingdom are more distributed in Cycling. and that the Medals from other countries are very evenly distributed among the five events
lastly. when comparing the medals won for different age group by gender, it was revealed that in general for both gender, age bracket from 20-40 and 40 to 60 in general has the most proporiton of medal won compared to other age group for gold, silver and bronze medal won.

# References

Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source
  Software, 4(43), 1686, https://doi.org/10.21105/joss.01686

H. Wickham. ggplot2: Elegant Graphics for Data Analysis. Springer-Verlag
  New York, 2016.

Hadley Wickham, Romain François, Lionel Henry and Kirill Müller (2021).
  dplyr: A Grammar of Data Manipulation. R package version 1.0.6.
  https://CRAN.R-project.org/package=dplyr

David Robinson, Alex Hayes and Simon Couch (2021). broom: Convert
  Statistical Objects into Tidy Tibbles. R package version 0.7.6.
  https://CRAN.R-project.org/package=broom

Arel-Bundock et al., (2018). countrycode: An R package to convert country
  names and country codes. Journal of Open Source Software, 3(28), 848,
  https://doi.org/10.21105/joss.00848

Silge J, Robinson D (2016). “tidytext: Text Mining and Analysis Using Tidy
Data Principles in R.” _JOSS_, *1*(3). doi: 10.21105/joss.00037 (URL:
https://doi.org/10.21105/joss.00037), <URL:
http://dx.doi.org/10.21105/joss.00037>.

  Simon Garnier, Noam Ross, Robert Rudis, Antônio P. Camargo, Marco Sciaini,
  and Cédric Scherer (2021). Rvision - Colorblind-Friendly Color Maps for R.
  R package version 0.6.0.

South, Andy 2011 rworldmap: A New R package for Mapping Global Data. The R
  Journal Vol. 3/1 : 35-43.

  D. Kahle and H. Wickham. ggmap: Spatial Visualization with ggplot2. The R
  Journal, 5(1), 144-161. URL
  http://journal.r-project.org/archive/2013-1/kahle-wickham.pdf

Original S code by Richard A. Becker, Allan R. Wilks. R version by Ray
  Brownrigg. Enhancements by Thomas P Minka and Alex Deckmyn. (2018). maps:
  Draw Geographical Maps. R package version 3.3.0.
  https://CRAN.R-project.org/package=maps

Pebesma, E.J., R.S. Bivand, 2005. Classes and methods for spatial data in
  R. R News 5 (2), https://cran.r-project.org/doc/Rnews/.

  Roger S. Bivand, Edzer Pebesma, Virgilio Gomez-Rubio, 2013. Applied spatial
  data analysis with R, Second edition. Springer, NY. https://asdar-book.org/

Roger Bivand and Nicholas Lewin-Koh (2021). maptools: Tools for Handling Spatial Objects.
  R package version 1.1-1. https://CRAN.R-project.org/package=maptools
  
Baptiste Auguie (2017). gridExtra: Miscellaneous Functions
  for "Grid" Graphics. R package version 2.3.
  https://CRAN.R-project.org/package=gridExtra
 
R Core Team (2021). R: A language and environment for
  statistical computing. R Foundation for Statistical
  Computing, Vienna, Austria. URL https://www.R-project.org/.
 
Hadley Wickham and Dana Seidel (2020). scales: Scale
  Functions for Visualization. R package version 1.1.1.
  https://CRAN.R-project.org/package=scales
 
Joe Cheng, Bhaskar Karambelkar and Yihui Xie (2021).
  leaflet: Create Interactive Web Maps with the JavaScript
  'Leaflet' Library. R package version 2.0.4.1.
  https://CRAN.R-project.org/package=leaflet
 
Hao Zhu (2021). kableExtra: Construct Complex Table with
  'kable' and Pipe Syntax. R package version 1.3.4.
  https://CRAN.R-project.org/package=kableExtra
 
Bob Rudis (2020). hrbrthemes: Additional Themes, Theme
  Components and Utilities for 'ggplot2'. R package version
  0.8.0. https://CRAN.R-project.org/package=hrbrthemes
 
Jason Cory Brunson and Quentin D. Read (2020). ggalluvial:
  Alluvial Plots in 'ggplot2'. R package version 0.12.3.
  http://corybrunson.github.io/ggalluvial/
 
Jeroen Ooms (2021). gifski: Highest Quality GIF Encoder. R
  package version 1.4.3-1.
  https://CRAN.R-project.org/package=gifski
 
Thomas Lin Pedersen and David Robinson (2020). gganimate: A
  Grammar of Animated Graphics. R package version 1.0.7.
  https://CRAN.R-project.org/package=gganimate
 
Erich Neuwirth (2014). RColorBrewer: ColorBrewer Palettes.
  R package version 1.1-2.
  https://CRAN.R-project.org/package=RColorBrewer
 
Csardi G, Nepusz T: The igraph software package for complex
  network research, InterJournal, Complex Systems 1695. 2006.
  https://igraph.org
 
Thomas Lin Pedersen (2021). ggraph: An Implementation of
  Grammar of Graphics for Graphs and Networks. R package
  version 2.0.5. https://CRAN.R-project.org/package=ggraph
  
Hadley Wickham and Jim Hester (2020). readr: Read
  Rectangular Text Data. R package version 1.4.0.
  https://CRAN.R-project.org/package=readr

Elmenshawy, A. R., Machin, D. R., & Tanaka, H. (2015). A rise in peak performance age in female athletes. Age, 37(3), 1-8.

Kaggle.com. 2021. 120 years of Olympic history: athletes and results. [online] Available at:
  <https://www.kaggle.com/heesoo37/120-years-of-olympic-history-athletes-and-results>
  [Accessed 23 May 2021].
  
Countries [ Latitude & Longitude ]. (2020, April 16). Kaggle. https://www.kaggle.com/franckepeixoto/countries